Continuous time

### 2023-09-28 continuous-time.qmd
fix #9

## Data
Load the data and remove observations that occurred more than 3 hours into a session.
```{r}
#| label: load-data
dat <- read_rds("data/data-raw.rds")
dat <- dat |>
  mutate(
    duration = duration - duration[1],
    hours = duration / 60,
    .by = c(pid, session)
  ) |>
  mutate(
    ps = interaction(pid, session, sep = "_")
  ) |>
  filter(prompt == "Wellbeing")

dat <- dat |>
  filter(
    !is.na(mood),
    hours <= 3
  ) |>
  mutate(
    cl = case_when(
      mood == 0 ~ "left",
      mood == 1 ~ "right",
      TRUE ~ "none"
    ),
    mood100 = mood * 100
  )
if (!is.na(N_SUBSET)) {
  pid_subset <- sample(unique(dat$pid), N_SUBSET)
  dat <- filter(dat, pid %in% pid_subset) |> 
    droplevels()
}
```

@@

```{r}
#| label: tbl-session-max-prop
#| tbl-cap: Proportion of participants that had at least on session last longer than gt_* hours
dat |> 
  summarise(
    max = max(hours), .by = c(pid)
  ) |> 
  summarise(
    gt_0.33 = mean(max > 0.33),
    gt_0.71 = mean(max > 0.716),
    gt_1 = mean(max > 1),
    gt_2 = mean(max > 2),
  ) |> 
  kable(digits = 2)
```

@tbl-session-max-prop shows that 66% of the participant have at least one session that lasted for over 0.71 hours. So we will base our knot placement on these quantiles.

```{r}
#| label: define-spline
#| code-fold: show
ns4 <- function(x) {
  ns(
    x,
    knots = c(0.05, 0.33, 0.7),
    Boundary.knots = c(0, 3)
  )
}
```

@@

```{r}
#| label: lmm-ns4
#| code-fold: show
fit <- fit_cached(
  "models/lmm-ns4.Rds",
  lmer(
    mood100 ~ ns4(hours) + (1 | ps) + (1 + ns4(hours) | pid),
    data = dat
  )
)
```

@@

p_change <- d_change |>
  ggplot(aes(hours, estimate)) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL
    ),
    alpha = 0.25
  ) +
  lims(y = c(0, 6)) +
  labs(x = "Session duration (hours)") +
  scale_x_hours
p_change
```

@tbl-change-contrast shows the estimated change from baseline after 10min, 30 min, 1 hour, 2 hours, and 3 hours.
```{r}
#| label: tbl-change-contrast
#| tbl-cap: Estimated change from baseline
emmeans(
  fit,
  ~hours,
  at = list(hours = c(0, 10 / 60, 0.5, 1, 2, 3)),
  lmer.df = "asymptotic"
) |>
  emmeans::contrast(
    method = "trt.vs.ctrl",
    ref = "hours0",
  ) |>
  confint() |>
  kable(
    digits = 2
  )
```

@@

```{r}
#| label: lmer-pre-interaction
#| code-fold: show
dat_pre <- dat |>
  filter(
    # Session has a wellbeing measure at time = 0
    duration[1] == 0,
    .by = c(pid, session)
  ) |>
  mutate(
    pre = mood100[1],
    .by = c(pid, session)
  ) |>
  filter(
    hours != 0
  ) |> 
  droplevels()

fit3 <- fit_cached(
  "models/lmm-pre-interaction.Rds",
  lmer(
    mood100 ~ ns4(hours) * ns(pre, 5) + (1 + ns4(hours) | pid) + (1 | ps),
    data = dat_pre
  )
)
```

@@

Calculate pre values we are interested in plotting.

@@

```{r}
#| label: tbl-pre-sd-values
#| tbl-cap: Distribution of average mood levels at the start of a session
pre_values <- pre_sum$mean + pre_sds * pre_sum$sd
data.frame(
  pre = pre_values,
  label = pre_labels
  ) |> 
  kable(digits = 2)
```

Plot the interaction at different pretest values. As shown in @fig-lmm-pre-interaction, this interaction model shows a pattern similar to @fig-intercept-sds where those who report lower mood at the beginning of a session also improve more. 
```{r}
#| label: fig-lmm-pre-interaction
#| fig-cap: Interaction between pretest mood and change, shown at -2 SD, -1, SD, the mean, and +1 SD.
#| fig-height: 3
#| fig-width: 8
emm <- emmeans(
  fit3,
  ~ hours + pre,
  at = list(
    hours = seq(0, 3, length.out = 100),
    pre = pre_values
  ),
  lmer.df = "asymp"
)
p_pre_x <- as.data.frame(emm) |>
  mutate(
    pre = factor(
      round(pre), 
      labels = pre_labels
      )
  ) |>
  ggplot(
    aes(
      hours,
      emmean,
      group = pre,
      color = pre
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL,
      fill = pre,
      color = NULL
    ),
    alpha = 0.25,
    show.legend = FALSE
  ) +
  color_scale +
  scale_x_hours

@@

Let's also calculate the within-session change for the interaction model.
```{r}
#| label: fig-lmm-pre-interaction-change
#| fig-cap: Within-session change from the interaction model
#| fig-height: 2.5
#| fig-width: 8
source("R/get_change_by_pre.R")
d_x_change <- data.frame(
  pre = round(pre_values),
  label = pre_labels
) |>
  pmap(\(pre, label) get_change_by_pre(
    pre,
    label,
    fit3,
    hours = seq(0, 3, length.out = 100)
  )) |>
  bind_rows()

p_pre_x_change <- d_x_change |>
  mutate(
    label = factor(
      label,
      levels = pre_labels
    )
  ) |>
  ggplot(
    aes(
      hours,
      estimate,
      group = label,
      color = label,
      fill = label
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL,
      color = NULL
    ),
    alpha = 0.15,
    show.legend = FALSE
  ) +
  geom_hline(
    yintercept = 0,
    linetype = "dotted"
  ) +
  labs(x = "Session duration (hours)") +
  color_scale +
  scale_x_hours +
  facet_wrap(~label, ncol = 4) 
p_pre_x_change
```

@@

And a table.
```{r}
#| label: tbl-pre-interaction-change
#| tbl-cap: Estimated within-session change from the interaction model
pre_sds <- c(1, 0, -1, -2)
tbl_x_change <- data.frame(
  pre = round(pre_values),
  label = pre_labels
) |>
  pmap(\(pre, label) get_change_by_pre(
    pre, 
    label, 
    fit3, 
    hours = c(0, 10/60, 0.5, 1, 2))
    ) |>
  bind_rows() |> 
  select(
    label, 
    pre, 
    hours,
    estimate, 
    CI_lwr = asymp.LCL, 
    CI_upr = asymp.UCL
    )
tbl_x_change |> 
  kable(digits = 2)
```

@@

```{r}
#| label: brms-cens
#| results: hide
set.seed(345345)
tmp <- filter(
  dat,
  pid %in% sample(unique(pid), n_pids_sample)
)

@@

```{r}
#| label: fig-cens-compare
#| fig-cap: Estimated trends with and without censoring.
#| fig-height: 3
#| fig-width: 8
d_brms <-
  emmeans(
    fit_b,
    ~hours,
    at = list(hours = seq(0, 3, length.out = 100))
  ) |>
  as.data.frame() |>
  mutate(model = "cens") |>
  select(
    hours,
    emmean,
    model,
    lower = "lower.HPD",
    upper = "upper.HPD"
  )
# SHIFT <- 0.017
SHIFT <- 0
d_lmm <-
  emmeans(
    fit2,
    ~hours,
    at = list(hours = seq(0, 3, length.out = 100))
  ) |>
  as.data.frame() |>
  select(
    hours,
    emmean,
    lower = "asymp.LCL",
    upper = "asymp.UCL"
  ) |>
  mutate(
    model = "lmm",
    emmean = emmean + SHIFT,
    upper = upper + SHIFT,
    lower = lower + SHIFT
  )
rbind(d_brms, d_lmm) |>
  ggplot(
    aes(
      hours,
      emmean,
      group = model,
      color = model
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper,
      fill = model,
      color = NULL
    ),
    alpha = 0.25
  ) +
  labs(x = "Session duration (hours)")
```

@@

We then compare the censored normal model with the LMM and recreate @fig-lmm-pre-interaction. As shown in @fig-cens-pre-interaction, there's almost no difference between the models. The LMMs CIs are slightly narrower near the intercept.
```{r}
#| label: fig-cens-pre-interaction
#| fig-cap: Censored normal vs LMM with a continuous by continuous interaction between within-session change and pretest mood.
#| fig-height: 3
#| fig-width: 8
get_emm_pre <- function(fit) {
  emmeans(
    fit,
    ~ hours + pre,
    at = list(
      hours = seq(0, 3, length.out = 100),
      pre = c(
        pre_sum$mean - 2 * pre_sum$sd,
        pre_sum$mean - pre_sum$sd,
        pre_sum$mean,
        pre_sum$mean + pre_sum$sd
      )
    ),
    lmer.df = "asymp"
  )
}
pre_sum <- tmp_pre |>
  summarise(
    pre_mean = median(pre), .by = pid
  ) |>
  summarise(
    mean = mean(pre_mean), sd = sd(pre_mean)
  )
emm_cens <- get_emm_pre(fit3_b) |>
  as.data.frame() |>
  mutate(
    model = "cens"
  ) |>
  rename(
    lwr = lower.HPD,
    upr = upper.HPD
  )
emm_lmm <- get_emm_pre(fit3_small) |>
  as.data.frame() |>
  mutate(
    model = "LMM"
  ) |>
  rename(
    lwr = asymp.LCL,
    upr = asymp.UCL
  )

@@

```{r}
#| label: fig-lmm-pre-interaction-sens-pre
#| fig-cap: Estimated trends for various functional forms of `pre`
tmp_models <- list()
tmp_models[["linear"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-pre-linear.Rds",
  lmer(
    mood100 ~ ns4(hours) * pre + (1 + ns4(hours) | pid) + (1 | ps),
    data = dat_pre
  )
)
tmp_models[["ns2"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns2.Rds",
    lmer(
      mood100 ~ ns4(hours) * ns(pre, 2) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns3"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns3.Rds",
    lmer(
      mood100 ~ ns4(hours) * ns(pre, 3) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns4"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns4.Rds",
    lmer(
      mood100 ~ ns4(hours) * ns(pre, 4) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns5"]] <- fit3

get_trend_by_model <- function(fit, model_label) {
  emm <- emmeans(
    fit,
    ~ hours + pre,
    at = list(
      hours = seq(0, 3, length.out = 100),
      pre = pre_values
    ),
    lmer.df = "asymp"
  )
  as.data.frame(emm) |>
    mutate(
      pre = factor(
        round(pre),
        labels = pre_labels,
      ),
      model = model_label
    )
}
tmp_p <- map2(
  tmp_models,
  names(tmp_models),
  \(fit, lab) get_trend_by_model(fit, lab)
) |>
  bind_rows()
p_pre_x_sens <- tmp_p |>
  ggplot(
    aes(
      hours,
      emmean,
      group = interaction(model, pre),
      color = model,
      linetype = pre
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL,
      fill = model,
      color = NULL
    ),
    alpha = 0.10,
    show.legend = FALSE
  ) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  scale_x_hours
p_pre_x_sens
```

@@

```{r}
#| label: fig-lmm-pre-interaction-sens-hours
#| fig-cap: Estimated trends for various functional forms of `hours`  
tmp_models2 <- list()
tmp_models2[["linear"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-linear.Rds",
  lmer(
    mood100 ~ hours * ns(pre, 5) + (1 + hours | pid) + (1 | ps),
    data = dat_pre
  )
)
tmp_models2[["ns2"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-hours-ns2.Rds",
    lmer(
      mood100 ~ ns(hours, 2) * ns(pre, 5) + (1 + ns(hours, 2) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models2[["ns3"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-n3.Rds",
  lmer(
    mood100 ~ ns(hours, 3) * ns(pre, 5) + (1 + ns(hours, 3) | pid) + (1 | ps),
    data = dat_pre,
  )
)
tmp_models2[["poly2"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-poly2.Rds",
  lmer(
    mood100 ~ poly(hours, 2) * ns(pre, 5) + (1 + poly(hours, 2) | pid) + (1 | ps),
    data = dat_pre,
  )
)
tmp_models2[["ns4"]] <- fit3
tmp_p <- map2(
  tmp_models2,
  names(tmp_models2),
  \(fit, lab) get_trend_by_model(fit, lab)
) |>
  bind_rows()
p_pre_x_sens %+% tmp_p 
```

>>>>

## Data
Load the data and remove observations that occurred more than 3 hours into a session.
```{r}
#| label: load-data
dat <- read_rds("data/data.rds")

dat <- dat |>
  filter(
    !is.na(mood),
    hours <= 3
  ) |>
  mutate(
    cl = case_when(
      mood == 0 ~ "left",
      mood == 100 ~ "right",
      TRUE ~ "none"
    ),
  )
if (!is.na(N_SUBSET)) {
  pid_subset <- sample(unique(dat$pid), N_SUBSET)
  dat <- filter(dat, pid %in% pid_subset) |> 
    droplevels()
}
```

@@

```{r}
#| label: tbl-session-max-prop
#| tbl-cap: Proportion of participants that had at least one session last longer than gt_* hours
dat |>
  summarise(
    max = max(hours),
    .by = c(pid)
  ) |>
  summarise(
    gt_0.18 = mean(max > 0.18),
    gt_0.51 = mean(max > 0.51),
    gt_1.3 = mean(max > 1.3),
    gt_2 = mean(max > 2),
  ) |>
  kable(digits = 2)
```

@tbl-session-max-prop shows that 85% of the participant have at least one session that lasted for over 0.51 hours, and 64% for over 1.3 hours. So we will base our knot placement on these quantiles.

```{r}
#| label: define-spline
#| code-fold: show
ns4 <- function(x) {
  ns(
    x,
    knots = c(0.18, 0.5, 1.3),
    Boundary.knots = c(0, 3)
  )
}
```

@@

```{r}
#| label: lmm-ns4
#| code-fold: show
fit <- fit_cached(
  "models/lmm-ns4.Rds",
  lmer(
    mood ~ ns4(hours) + (1 | ps) + (1 + ns4(hours) | pid),
    data = dat
  )
)
```

@@

p_change <- d_change |>
  ggplot(aes(hours, estimate)) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL
    ),
    alpha = 0.25
  ) +
  lims(y = c(0, 10)) +
  labs(x = "Session duration (hours)") +
  scale_x_hours
p_change
```

@tbl-change-contrast shows the estimated change from baseline after 15min, 30 min, 1 hour, 2 hours, and 3 hours.
```{r}
#| label: tbl-change-contrast
#| tbl-cap: Estimated change from baseline
emmeans(
  fit,
  ~hours,
  at = list(hours = c(0, 15 / 60, 0.5, 1, 2, 3)),
  lmer.df = "asymptotic"
) |>
  emmeans::contrast(
    method = "trt.vs.ctrl",
    ref = "hours0",
  ) |>
  confint() |>
  kable(
    digits = 2
  )
```

@@

```{r}
#| label: lmer-pre-interaction
#| code-fold: show
dat_pre <- dat |>
  filter(
    # Session has a wellbeing measure at time = 0
    hours[1] == 0,
    .by = c(pid, session)
  ) |>
  mutate(
    pre = mood[1],
    .by = c(pid, session)
  ) |>
  filter(
    hours > 0
  ) |> 
  droplevels()

fit3 <- fit_cached(
  "models/lmm-pre-interaction.Rds",
  lmer(
    mood ~ ns4(hours) * ns(pre, 5) + (1 + ns4(hours) | pid) + (1 | ps),
    data = dat_pre
  )
)
```

@@

Next we'll calculate the pre values we are interested in plotting.

@@

However, baseline mood is not normally distributed, so we'll use percentiles instead. 
```{r}
#| label: tbl-pre-sd-values
#| tbl-cap: Distribution of average mood levels at the start of a session
#pre_values <- pre_sum$mean + pre_sds * pre_sum$sd

pre <- dat_pre |> 
  summarise(pre = pre[1], .by = ps) |> 
  pull(pre)
pre_values <- quantile(pre, c(0.05, .25, 0.5, 0.75))
pre_labels_x <- c("5th", "25th", "Median", "75th")
colors <- c(
  "5th" = "#4daf4a",
  "25th" = "#e41a1c",
  "75th" = "#377eb8",
  "Median" = "#000000"
)
color_scale_x <- list(
  scale_color_manual(
    "Pre",
    values = colors
  ),
    scale_fill_manual(
    "Pre",
    values = colors
  )
)
data.frame(
  pre = pre_values,
  label = pre_labels_x
  ) |> 
  kable(digits = 2)
```

Plot the interaction at different pretest values. As shown in @fig-lmm-pre-interaction, this interaction model shows a pattern similar to @fig-intercept-sds where those who report lower mood at the beginning of a session also improve more. 
```{r}
#| label: fig-lmm-pre-interaction
#| fig-cap: Interaction between pretest mood and change, shown at -2 SD, -1, SD, the mean, and +1 SD.
#| fig-height: 3
#| fig-width: 8
emm <- emmeans(
  fit3,
  ~ hours + pre,
  at = list(
    hours = seq(0, 3, length.out = 100),
    pre = pre_values
  ),
  lmer.df = "asymptotic"
)
p_pre_x <- as.data.frame(emm) |>
  mutate(
    pre = factor(
      round(pre), 
      labels = pre_labels_x
      )
  ) |>
  ggplot(
    aes(
      hours,
      emmean,
      group = pre,
      color = pre
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL,
      fill = pre,
      color = NULL
    ),
    alpha = 0.25,
    show.legend = FALSE
  ) +
  color_scale_x +
  scale_x_hours

@@

Let's also calculate the within-session change for the interaction model.
```{r}
#| label: fig-lmm-pre-interaction-change
#| fig-cap: Within-session change from the interaction model
#| fig-height: 2.5
#| fig-width: 8
source("R/get_change_by_pre.R")
d_x_change <- data.frame(
  pre = round(pre_values),
  label = pre_labels_x
) |>
  pmap(\(pre, label) get_change_by_pre(
    pre,
    label,
    fit3,
    hours = seq(0, 3, length.out = 100)
  )) |>
  bind_rows()

p_pre_x_change <- d_x_change |>
  mutate(
    label = factor(
      label,
      levels = pre_labels_x
    )
  ) |>
  ggplot(
    aes(
      hours,
      estimate,
      group = label,
      color = label,
      fill = label
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL,
      color = NULL
    ),
    alpha = 0.15,
    show.legend = FALSE
  ) +
  geom_hline(
    yintercept = 0,
    linetype = "dotted"
  ) +
  labs(x = "Session duration (hours)") +
  color_scale_x +
  scale_x_hours +
  facet_wrap(~label, ncol = 4) 
p_pre_x_change
```

@@

And a table.
```{r}
#| label: tbl-pre-interaction-change
#| tbl-cap: Estimated within-session change from the interaction model
pre_sds <- c(1, 0, -1, -2)
tbl_x_change <- data.frame(
  pre = round(pre_values),
  label = pre_labels_x
) |>
  pmap(\(pre, label) get_change_by_pre(
    pre, 
    label, 
    fit3, 
    hours = c(0, 15/60, 0.5, 1, 2))
    ) |>
  bind_rows() |> 
  select(
    label, 
    pre, 
    hours,
    estimate, 
    CI_lwr = asymp.LCL, 
    CI_upr = asymp.UCL
    )
tbl_x_change |> 
  kable(digits = 2)
```

@@

```{r}
#| label: brms-cens
#| results: hide
set.seed(345345)
tmp <- filter(
  dat,
  pid %in% sample(unique(pid), n_pids_sample)
) |> 
  mutate(mood = mood / 100)

@@

```{r}
#| label: fig-cens-compare
#| fig-cap: Estimated trends with and without censoring.
#| fig-height: 3
#| fig-width: 8
d_brms <-
  emmeans(
    fit_b,
    ~hours,
    at = list(hours = seq(0, 3, length.out = 100))
  ) |>
  as.data.frame() |>
  mutate(model = "cens") |>
  select(
    hours,
    emmean,
    model,
    lower = "lower.HPD",
    upper = "upper.HPD"
  )
d_lmm <-
  emmeans(
    fit2,
    ~hours,
    at = list(hours = seq(0, 3, length.out = 100)),
    lmer.df = "asymptotic"
  ) |>
  as.data.frame() |>
  select(
    hours,
    emmean,
    lower = "asymp.LCL",
    upper = "asymp.UCL"
  ) |>
  mutate(
    model = "lmm",
    emmean = emmean,
    upper = upper,
    lower = lower
  )
rbind(d_brms, d_lmm) |>
  ggplot(
    aes(
      hours,
      emmean,
      group = model,
      color = model
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper,
      fill = model,
      color = NULL
    ),
    alpha = 0.25
  ) +
  labs(x = "Session duration (hours)")
```

@@

We then compare the censored normal model with the LMM and recreate @fig-lmm-pre-interaction. As shown in @fig-cens-pre-interaction, there's almost no difference between the models.
```{r}
#| label: fig-cens-pre-interaction
#| fig-cap: Censored normal vs LMM with a continuous by continuous interaction between within-session change and pretest mood.
#| fig-height: 3
#| fig-width: 8
get_emm_pre <- function(fit) {
  emmeans(
    fit,
    ~ hours + pre,
    at = list(
      hours = seq(0, 3, length.out = 100),
      pre = c(
        pre_sum$mean - 2 * pre_sum$sd,
        pre_sum$mean - pre_sum$sd,
        pre_sum$mean,
        pre_sum$mean + pre_sum$sd
      )
    ),
    lmer.df = "asymp"
  )
}
pre_sum <- tmp_pre |>
  summarise(
    pre_mean = median(pre), .by = pid
  ) |>
  summarise(
    mean = mean(pre_mean), sd = sd(pre_mean)
  )
emm_cens <- get_emm_pre(fit3_b) |>
  as.data.frame() |>
  mutate(
    model = "cens"
  ) |>
  rename(
    lwr = lower.HPD,
    upr = upper.HPD
  )
emm_lmm <- get_emm_pre(fit3_small) |>
  as.data.frame() |>
  mutate(
    model = "LMM"
  ) |>
  rename(
    lwr = asymp.LCL,
    upr = asymp.UCL
  )

@@

```{r}
#| label: fig-lmm-pre-interaction-sens-pre
#| fig-cap: Estimated trends for various functional forms of `pre`
tmp_models <- list()
tmp_models[["linear"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-pre-linear.Rds",
  lmer(
    mood ~ ns4(hours) * pre + (1 + ns4(hours) | pid) + (1 | ps),
    data = dat_pre
  )
)
tmp_models[["ns2"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns2.Rds",
    lmer(
      mood ~ ns4(hours) * ns(pre, 2) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns3"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns3.Rds",
    lmer(
      mood ~ ns4(hours) * ns(pre, 3) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns4"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-pre-ns4.Rds",
    lmer(
      mood ~ ns4(hours) * ns(pre, 4) + (1 + ns4(hours) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models[["ns5"]] <- fit3

get_trend_by_model <- function(fit, model_label) {
  emm <- emmeans(
    fit,
    ~ hours + pre,
    at = list(
      hours = seq(0, 3, length.out = 100),
      pre = pre_values
    ),
    lmer.df = "asymp"
  )
  as.data.frame(emm) |>
    mutate(
      pre = factor(
        round(pre),
        labels = pre_labels_x,
      ),
      model = model_label
    )
}
tmp_p <- map2(
  tmp_models,
  names(tmp_models),
  \(fit, lab) get_trend_by_model(fit, lab)
) |>
  bind_rows()
p_pre_x_sens <- tmp_p |>
  ggplot(
    aes(
      hours,
      emmean,
      group = interaction(model, pre),
      color = model,
      linetype = pre
    )
  ) +
  geom_line() +
  geom_ribbon(
    aes(
      ymin = asymp.LCL,
      ymax = asymp.UCL,
      fill = model,
      color = NULL
    ),
    alpha = 0.10,
    show.legend = FALSE
  ) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  scale_x_hours
p_pre_x_sens
```

@@

```{r}
#| label: fig-lmm-pre-interaction-sens-hours
#| fig-cap: Estimated trends for various functional forms of `hours`  
tmp_models2 <- list()
tmp_models2[["linear"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-linear.Rds",
  lmer(
    mood ~ hours * ns(pre, 5) + (1 + hours | pid) + (1 | ps),
    data = dat_pre
  )
)
tmp_models2[["ns2"]] <-
  fit_cached(
    "models/lmm-pre-interaction-sens-hours-ns2.Rds",
    lmer(
      mood ~ ns(hours, 2) * ns(pre, 5) + (1 + ns(hours, 2) | pid) + (1 | ps),
      data = dat_pre,
    )
  )
tmp_models2[["ns3"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-n3.Rds",
  lmer(
    mood ~ ns(hours, 3) * ns(pre, 5) + (1 + ns(hours, 3) | pid) + (1 | ps),
    data = dat_pre,
  )
)
tmp_models2[["poly2"]] <- fit_cached(
  "models/lmm-pre-interaction-sens-hours-poly2.Rds",
  lmer(
    mood ~ poly(hours, 2) * ns(pre, 5) + (1 + poly(hours, 2) | pid) + (1 | ps),
    data = dat_pre,
  )
)
tmp_models2[["ns4"]] <- fit3
tmp_p <- map2(
  tmp_models2,
  names(tmp_models2),
  \(fit, lab) get_trend_by_model(fit, lab)
) |>
  bind_rows()
p_pre_x_sens %+% tmp_p 
```
